Defocus Corrected Large Area Cryo-EM (DeCo-LACE) for Label-Free Detection of Molecules across Entire Cell Sections

### 2022-11-03 reviews/submitted.tex
almost there

@@

\leavevmode\vadjust pre{\hypertarget{ref-kncnYGLD}{}}%
\CSLLeftMargin{25. }%
\CSLRightInline{\textbf{Shedding light on the cell biology of extracellular vesicles}
\CSLBlock{Guillaume van Niel, Gisela D'Angelo, Graça Raposo} \emph{Nature Reviews Molecular Cell Biology} (2018-01-17) \url{https://doi.org/gct4df}
\CSLBlock{DOI: \href{https://doi.org/10.1038/nrm.2017.125}{10.1038/nrm.2017.125} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/29339798}{29339798}}}

>>>>

¶ ¶ ¶ ¶ ¶ ¶ ¶ ¶ ¶ ¶ ¶ ¶ ¶ ¶ ¶ ¶ ¶ ¶ ¶ ¶ ¶ ¶ ¶ ¶ ¶ ¶ ¶ ¶ ¶ ¶ ¶ ¶ ¶ ¶
¶ ¶

@@

\leavevmode\vadjust pre{\hypertarget{ref-kncnYGLD}{}}%
\CSLLeftMargin{25. }%
\CSLRightInline{\textbf{Shedding light on the cell biology of extracellular vesicles}
\CSLBlock{Guillaume van Niel, Gisela D\textquotesingle Angelo, Graça Raposo} \emph{Nature Reviews Molecular Cell Biology} (2018-01-17) \url{https://doi.org/gct4df}
\CSLBlock{DOI: \href{https://doi.org/10.1038/nrm.2017.125}{10.1038/nrm.2017.125} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/29339798}{29339798}}}
